Constrained Natural Language Parser for Semantic Web Based Policies

### 2009-08-13 paper/paper.tex
modified the abstract a bit

We propose a system which is capable of translating a constrained natural language sentence describing a policy or a rule into the equivalent RDF representation. In our proof of concept implementation we use a template to convert sentences describing a human-readable rule or a policy into a machine-readable policy expressed in the Accountability In RDF (AIR) policy language. The sentences are parsed using a feature-based context-free grammar which extracts semantic information contained in the policy given in natural language to build a parse tree. The information contained in the parse tree are then processed to build the AIR policy. AIR policies are represented as Turtle statements and can be used to express security and privacy constraints in terms of different ontologies.

We present a Firefox sidebar extension as the user interface for this system, and we believe that it provides a natural interface for users for authoring policies in RDF.

>>>>

In this paper, we propose the Policy Parser, a system for translating
policies and rules in a natural language into an equivalent RDF
representation. The Policy Parser uses
templates to convert informal but structurally-constrained sentences into 
machine-readable policies, which are expressed in the
Accountability In RDF (AIR) policy language. A sentence is parsed
using a feature-based context-free grammar, which extracts semantic
information from the sentence to build a corresponding parse tree. The
information contained in the parse tree is then processed to build
an AIR policy. AIR policies are represented as Turtle statements and
can be used to express security and privacy constraints in a variety
of ontologies. We present a Firefox sidebar extension as the user interface for this
system, and we believe that it provides a natural interface for authoring
policies in RDF.
